%=============================================================
% One-Page Resume — Idhaya Bastine Kennedy
% Compiler: pdfLaTeX (default in Overleaf)
%=============================================================
\documentclass[11pt, a4paper]{article}

\usepackage{newtxtext, newtxmath}
\usepackage[a4paper, top=0.6in, bottom=0.6in, left=0.7in, right=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{parskip}
\usepackage{microtype}

\pagestyle{empty}
\setlength{\parskip}{0pt}

% Section headings
\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{7pt}{4pt}

% Bullet list spacing
\setlist[itemize]{leftmargin=1.5em, itemsep=2pt, topsep=2pt, parsep=0pt}

%=============================================================
\begin{document}

%-------------------------------------------------------------
% HEADER
%-------------------------------------------------------------
\begin{center}
  {\LARGE\bfseries Idhaya Bastine Kennedy}\\[5pt]
  \small
  Dublin 16, Ireland \ $|$ \ +353 892 585 050 \ $|$ \
  \href{mailto:idhayakennedy3@email.com}{idhayakennedy3@email.com}\\[3pt]
  \href{https://linkedin.com/in/idhaya-bastine-kennedy-79b15b186}{linkedin.com/in/idhaya-bastine-kennedy} \ $|$ \
  \href{https://github.com/IdhayaBastine15}{github.com/IdhayaBastine15}\\[3pt]
  \textit{Right to Work: Ireland (Stamp 1G) --- No sponsorship required}
\end{center}

%-------------------------------------------------------------
% PROFILE
%-------------------------------------------------------------
\section{Profile}
\small
Full Stack Software Engineer with 3+ years of experience designing and delivering production-grade web applications in healthcare startup environments. Specialises in Node.js, React, Angular, and Python, with hands-on experience building REST APIs, microservices, and cloud-native systems on AWS. Proven track record of improving application performance by 20--30\%, supporting international product rollouts, and mentoring junior developers. Holds an MSc in Data Analytics (2:1) from National College of Ireland, Dublin.

%-------------------------------------------------------------
% TECHNICAL SKILLS
%-------------------------------------------------------------
\section{Technical Skills}
\small
\begin{tabular}{@{} >{\bfseries}p{3.0cm} @{\hspace{0.3cm}} p{13.0cm} @{}}
  Languages        & JavaScript (ES6+), TypeScript, Python, SQL \\[3pt]
  Frontend         & React, Angular, React Native, HTML5, CSS3, Responsive Design \\[3pt]
  Backend          & Node.js, Express.js, FastAPI, Flask, Django, REST APIs, Microservices \\[3pt]
  Databases        & PostgreSQL, MySQL, MongoDB, DynamoDB \\[3pt]
  Cloud \& DevOps  & AWS (EC2, S3, RDS, Lambda, API Gateway), Docker, Kubernetes, Jenkins, CI/CD \\[3pt]
  Tools            & Git, GitHub, GitHub Copilot, Jasmine, Mocha, Selenium, Agile/Scrum \\
\end{tabular}

%-------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%-------------------------------------------------------------
\section{Professional Experience}

\noindent
{\small\textbf{Full Stack Developer} \hfill \textit{Mar 2021 -- Oct 2023}}\\[-2pt]
{\small\textit{TRIAS, Bengaluru, India}}

\begin{itemize}\small
  \item Designed and delivered a production \textbf{Electronic Health Records (EHR) platform} end-to-end, managing patient demographics, medical history, diagnoses, treatment plans, and discharge summaries across GP, therapy, and specialist care departments.
  \item Supported the \textbf{international rollout} of the EHR system from India to Papua New Guinea, enabling adoption across multiple hospital facilities and contributing to product expansion into a new market.
  \item Developed and enhanced a \textbf{Laboratory Information System (LIS)} for a Canadian healthcare client, integrating secure data ingestion from medical devices including thermometers, temperature probes, and fetal monitoring systems.
  \item Improved application performance by \textbf{20--30\%} through backend optimisation, database indexing, query tuning, caching strategies, lazy loading, and reusable component architecture.
  \item Built and maintained \textbf{microservices-based REST APIs} using Node.js, Express.js, and Python, integrating PostgreSQL, MySQL, and MongoDB for efficient clinical data handling.
  \item Developed responsive \textbf{Angular and React} frontends aligned with clinical UX workflows, collaborating closely with UX/UI designers.
  \item Deployed services on \textbf{AWS} (EC2, S3, RDS, Lambda) using CI/CD pipelines via Jenkins and GitHub Actions to ensure reliable releases.
  \item Contributed to \textbf{architectural decisions and technical roadmap} in direct collaboration with the CEO and CTO.
  \item Conducted \textbf{code reviews} for junior developers and mentored 4--5 interns, enforcing coding standards and best practices.
\end{itemize}

\vspace{4pt}
\noindent
{\small\textbf{Intern --- Frontend Developer} \hfill \textit{Mar 2021 -- Jul 2021}}\\[-2pt]
{\small\textit{TRIAS, Bengaluru, India}}

\begin{itemize}\small
  \item Built a \textbf{Health Analytics module} for the EHR platform; designed and implemented a data processing algorithm to segregate paid/unpaid transactions across UPI, cash, and POS systems --- deployed live in a hospital environment.
  \item Developed a \textbf{Python Flask web interface} to visualise analytics workflows and support hospital finance operations.
\end{itemize}

%-------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------
\section{Education}

\noindent
{\small\textbf{MSc Data Analytics (2:1)} \hfill \textit{Jan 2024 -- Jan 2025}}\\[-2pt]
{\small\textit{National College of Ireland, Dublin, Ireland}}

\vspace{5pt}
\noindent
{\small\textbf{B.E. Mechanical Engineering} \hfill \textit{2016 -- 2020}}\\[-2pt]
{\small\textit{Loyola-ICAM College of Engineering and Technology, Chennai, India}}

%=============================================================
\end{document}
